---
name: Oriondrive
position: "Band / Mathematical Challenge"
address: "St. Louis, Missouri / Norrköping, Sweden"
www: archive.org/details/linfri-repo
date: "October 2020 - Present"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Biography

\  

Oriondrive began as a collaborative project between Thomas Jackson Park a.k.a. Mystified (St. Louis, Missouri) and Linn Ruth Friberg (Norrköping, Sweden) in 2020. Initially, the project's output consisted of abstract hip-hop music generated procedurally using GenerIter and interwoven with generative speech from a GPT-2 model fed into the speech synthesizer, including the cover artwork that was generated by GAN. The only aspect of music that wasn't generative was mixing and effects. Linn was also one of the beta testers for GenerIter in 2021.

\  

The project has found its musical identity and style in 2021 with the release of the album "3dd89f7d." Linn created a now-retired REST API for voice generation with the help of programming in R, a skill picked up during her time in the bachelor's program in statistics at Linköping University. As an experiment, she wrote down her intentions for 2022, generated CRC-32 hashes based on the strings with the intentions and fed the results to the API. The output was processed with the help of a vocoder and mixed together with selected electronic tracks by Thomas. 

\  

In 2022, the idea of integrating music and mathematical/research challenges took traction. Linn designed a challenge during the summer of 2022 that requires active listening and exercising skills in linear algebra and statistics at the undergraduate level. This challenge is perfect for students of statistics or applied mathematics, or anyone with basic knowledge of statistics and linear algebra. It can be solved using R (recommended), Python or MATLAB. Linn even incorporated a symbolic crypto prize for whoever solves it first. To solve the challenge, active listening to Oriondrive music is required.

\  

The music by Oriondrive is available as free downloads from the **[Internet Archive](https://archive.org/search.php?query=subject%3A%22oriondrive%22&and[]=subject%3A%22linn+friberg%22)**. As long as Oriondrive explores new ideas, the project will stay active.

\  

# Discography

```{r}
library(tibble)
tribble(
  ~ Album, ~ Year, ~ Label, 
  "Sustainable Security", "2020", "Treetrunk Records",
  "Healthy Growth", "2021", "Attenuation Circuit",
  "3dd89f7d", "2021", "Kalamine Records",
  "The Matrix", "2022", "TH_TIMEPEACE",
) %>% 
  detailed_entries(Album, Year, Label)

```

