---
name: Linn
surname: Friberg
position: "Statistics Student, App Developer"
address: "Location: Norrköping, Sweden"
github: linfri
linkedin: linfri
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
# Loading the libraries
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
library(readxl)

```

# About Me

 * Passionate about R development, including Shiny web apps and Plumber APIs;
 * Learning new things continuously in parallel with my university studies;
 * Planning my own side projects as microservices with data-driven approach;
 * Mastering the art of interdisciplinary collaboration, with proven record of projects;
 * Fluent in English and Swedish, elementary proficiency in Icelandic.  

\hfill\break

# Education

```{r}
# Description of my education
readxl::read_excel("education.xlsx") %>% detailed_entries(what = Degree,
                                                          when = Year,
                                                          with = Institution)

```

# Courses

```{r}
# Description of my courses
readxl::read_excel("courses.xlsx") %>% detailed_entries(what = Course,
                                                        when = Year,
                                                        with = Institution,
                                                        why = Code)

```

\hfill\break

# Certificates

```{r}
# Description of my certificates
readxl::read_excel("certificates.xlsx") %>% detailed_entries(what = Certificate,
                                                             when = Year,
                                                             with = Organisation,
                                                             where = Location,
                                                             why = Description)

```

\hfill\break

# Recent Work Experience

```{r}
# Description of my work experience
readxl::read_excel("experience.xlsx") %>% detailed_entries(what = Position,
                                                           when = Year,
                                                           with = Company,
                                                           where = Location,
                                                           why = Description)

```

